\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors

### 2021-08-13 Draft/Manuscript.tex
editys

\textbf{Plant strategies.} The phylogenetically informed principal
component analysis (pPCA) captured by the first two and three axes
51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
of 0.76. The first principal component (PC1) represented 26.72\% of the
trait variation and indicated a trade-off between flower number and
flower size. We refer to this axis as the `flower number - flower size
trade-off as already described in previous
studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
Hence, one end of the spectrum comprised species with high investment in
flower number and plant height but small flower size, short style length
and low ovule number. The other end of this spectrum comprised species
that were short in height and invested in large flowers, long styles,
many ovules, but few flowers. The main contributing traits to PC1 were
plant height, flower number, ovule number and flower size (loadings
\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
style length also contributed moderately on PC1 (loading = -0.33). The
second principal component (PC2) represented 25.05\% of the trait
variation and indicated a trade-off between low and high pollinator
dependence. We refer to this axis as the `pollinator dependence
trade-off'. The main driver of trait variation on PC2 was autonomous
selfing (loading = 0.85) but the other traits (except ovule number) also
made moderate contributions (loadings from 0.27 to 0.4; Supplementary
Table S3). We found that high pollinator dependence was associated with
larger and higher numbers of flowers, greater plant height and longer
styles. In contrast, species with high levels of autonomous selfing
tended to have fewer and smaller flowers, had shorter styles and were
shorter in height. Further, PC3 explained a considerable amount of trait
variability (19.17\%) and the main contributors to this axis were style
length (loading = -0.66) and the degree of autonomous selfing (loading =
-0.51). The remaining traits, apart from ovule number, were moderately
correlated to changes on PC3 (loadings from -0.23 to -0.46;
Supplementary Table S3). Thus, because style length was correlated with
all traits on PC3 and was the main driver of variation, we refer to this
axis as the `style length trade-off'. Further, the pPCA with the subset
of species that had nectar and pollen quantity data showed that nectar
quantity (microlitres of nectar per flower) was positively associated
with flower size, style length and ovule number (PC1, 23.40\%); and
pollen quantity (pollen grains per flower) was positively correlated
with flower number and plant height and negatively associated with
autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
explained similar variance with the first two principal components
(45.07\%) and similar associations of traits despite some variability in
the loadings (Supplementary Table S4).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{}} Life history
strategies for 1,236 plant species from 28 plant-pollinator networks
studies across the first two axes of trait variation from a
phylogenetically informed principal component analysis (pPCA). The solid
arrows indicate the direction of the different quantitative traits
(flower number, plant height, style length, flower size, ovule number
and level of autonomous selfing) in the 2-d plane. The length of the
arrows indicate the weight of the variables on each principal component
and the labelled icons at their end represent the extreme form of the
trait continuum. The dashed lines show the opposed direction of trait
variation and the non-labelled icons at their end illustrate the
opposing extreme of the continuum.}
\end{figure}

We found that most categorical traits were statistically associated with
the first two axes of trait variation (Fig. 2 and Supplementary Table
S2). Flower symmetry, which was only associated with PC2 (Sum of squares
= 8.51, F-value = 14.72, p \textless{} 0.01 ), and nectar provision,
which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37,
F-value = 0.29 , p = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, p
= 0.23) showed lack of statistical association. In addition, we found
statistical differences (Tukey test) between the different levels of
categorical traits in the trait space (Supplementary Fig. S7). Regarding
self compatibility, we found larger differences on PC2 (i.e., species
with unisexual flowers that were self incompatibile were statistically
differentiated from species with partial or full self compatibility;
Supplementary Fig. S7 A and B). Life forms differed statistically across
both axes of trait variation and followed a gradient of larger life
forms (trees and shrubs) with higher pollinator dependence to smaller
ones (herbs) with lower pollinator dependence (Supplementary Fig. S7 C
and D). Consequently, lifespan also followed this gradient but perennial
and short lived species only differed statistically on PC2
(Supplementary Fig. S7 E and F). Species with unisexual flowers
(monoecious and dioecious) were clustered on both extremes of the first
two principal components and had the highest pollinator dependence and
highest number of flowers (Supplementary Fig. S7 G and H). Moreover, we
found that the campanulate and capitulum flower shapes were
differentiated from tube, papilionaceous, open and brush shapes in the
trait space. The former morphologies had larger flowers and greater
pollinator dependence, while the latter had higher flower number and
greater autonomous selfing (Supplementary Fig. S7 I and J). Regarding
flower symmetry, zygomorphic flowers were associated with lower levels
of pollinator dependence, whereas actinomorphic flowers had higher
levels of pollinator dependence (Supplementary Fig. S7 K and L).

@@

\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
signal (P \textless{} 0.01) in all quantitative traits (Supplementary
Table S5). The traits that showed the highest phylogenetic signal were
ovule number (\(\lambda = 1\)), pollen grains per flower
(\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)), followed by
flower length (\(\lambda = 0.75\)), flower width (\(\lambda = 0.73\)),
number of flowers per plant (\(\lambda = 0.69\)) and nectar
concentration (\(\lambda = 0.65\)). The traits that showed a moderate
phylogenetic signal were inflorescence width (\(\lambda = 0.57\)), style
length (\(\lambda = 0.49\)) and autonomous selfing (\(\lambda = 0.34\)).
Finally, microliters of nectar per flower showed the lowest phylogenetic
signal of all traits (\(\lambda = 0.14\)).

\textbf{Visitation patterns.} The main axes of trait variation explained
little of the overall visitation rates (conditional \(R2 = 0.31\);
marginal \(R2 = 0.06\)) but showed relevant trends when we explored the
interaction with the different floral visitors guilds (Fig. 3). All
floral visitors guilds visited plant species with higher pollinator
dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
3f). Furthermore, when running an additional model that separates the
most represented families of Anthophila-Hymenoptera (bees;
\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
family Apidae was the main driver of the observed patterns
(Supplementary Fig. S8).

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 2 \textbar{} Fitted
posterior estimates of the number of visits made by the different floral
visitors guilds in relation to the three main axes of trait variation
(PC1, PC2 and PC3)}. Bees (a, b and c) and the rest of guilds (d, e and
f) were plotted separately for visualization purposes. In addition, we
trimmed the plotting area that was over the 95th percentile to improve
visualisation. PC1 represents the flower number - flower size trade-off,
PC2 represents the pollinator dependence trade-off and PC3, the style
length trade-off.}
\end{figure}

@@

\textbf{Plant species functional roles.} The three main axes of trait
variation poorly explain the variance of the different plant species
level metrics (Supplementary Fig. S9; interaction frequency
\textasciitilde{} PCs, \(conditional R2 = 0.11\),
\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
\textasciitilde{} PCs, \(conditional R2 = 0.37\),
\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
PC1 and PC3 for interaction frequency and specialization. On the flower
number - flower size trade-off (PC1), interaction frequency was higher
for plant species with more flowers but was lower for plant species with
larger flowers. On PC1, specialization showed the opposite trend. On the
style length trade-off (PC3), interaction frequency was lower for plants
with shorter styles and lower selfing and higher for species with long
styles and higher levels of selfing. Again, specialization showed the
opposite trend to interaction frequency.

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Regression
tree analysis of interaction frequency (log-transformed), normalized
degree and specialization for the subset of species with quantitative
data for pollen and nectar traits}. The superior value inside the node
indicates the mean value of the different species-level metric and the
lower value, the percentage of species that are considered in each node.
Thus, the top node has the mean value of the named trait for the 100\%
of species. Each node has a yes/no question and when the condition is
fulfilled, the branch turns to the `yes' direction and when not, to the
`no' direction. This rationale is followed in all the regression trees
as indicated in the first branch division of the topmost node of each
tree.}
\end{figure}

@@

Over 50\% of plant trait variation was captured by the flower number -
flower size and pollinator dependence trade-offs. Variation in these two
axes of trait variation appears to be associated with the commonly
described `fast-slow continuum' in
plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}} life
history strategies as indicated by the different floral and reproductive
traits associated with plant height, life form and lifespan. The
``slow'' part of the continuum (i.e., tall trees and shrubs) had plant
species with many flowers, few ovules, higher pollinator dependence,
greater occurrence of self-incompatibility and more complex breeding
systems (e.g., monoecious and dioecious species). In contrast, species
that employed the ``fast'' strategy (i.e., short herbs), had fewer
flowers, more ovules, greater occurrence of self compatibility and lower
pollinator dependence. Further, on the first two axes of trait
variation, we found additional support for the positive association
between outcrossing rate and floral display, in accordance with
\protect\hyperlink{ref-goodwillie2010}{24}. This trend was further
confirmed when looking at the specific correlation between floral
display and autonomous selfing for our dataset (see Supplementary Fig.
S10).

Despite the low predictive power of the main axes of trait variation on
overall visitation patterns, we found commonalities among and within
floral visitors guilds across these axes that indicate the influence of
life history strategies on floral visitation rate. For example, all
guilds showed an increasing trend of visitation on plant species with
higher pollinator dependence, which were also associated with larger
floral displays and greater pollen quantity (Fig. 1 and Supplementary
Fig. S6). This trend is consistent with previous plant-pollinator
studies that show higher visitation rates on species that make greater
reproductive
investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
In regard to the flower number - flower size and style length
trade-offs, different guilds showed contrasting visitation rates, which
could be associated with different pollination syndromes at a
macroecological scale. For instance, the guilds of bees and syrphids
were clearly associated with opposing life-strategies on PC1 and PC3
(Fig. 3) indicating a possible niche partitioning among these two
guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
However, these plant-pollinator associations do not account for some of
the traits (i.e., pollen and nectar quantity) that had greater relevance
on the species network roles (Fig. 4) because of insufficient data
availability and lack of pollinator efficiency measurements for more
complete descriptions of the pollination
syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
any case, it is worth noting that this general pattern emerges in
field-measured plant-pollinator networks, where other local factors such
as species relative abundances, will surely explain part of the observed
variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.

>>>>

\textbf{Plant strategies.} The phylogenetically informed principal
component analysis (pPCA) captured by the first two and three axes
51.8\% and 70.97\% of trait variation, respectively (Fig. 1 and
Supplementary Fig. S5) and had a phylogenetic correlation (\(\lambda\))
of 0.76. The first principal component (PC1) represented 26.72\% of the
trait variation and indicated a trade-off between flower number and
flower size. We refer to this axis as the `flower number - flower size
trade-off' as already described in previous
studies\textsuperscript{\protect\hyperlink{ref-sargent2007}{32},\protect\hyperlink{ref-kettle2011}{33}}.
Hence, one end of the spectrum comprised species with high investment in
flower number and plant height but small flower size, short style length
and low ovule number. The other end of this spectrum comprised species
that were short in height and invested in large flowers, long styles,
many ovules, but few flowers. The main contributing traits to PC1 were
plant height, flower number, ovule number and flower size (loadings
\textgreater{} \textbar{}0.5\textbar{}; Supplementary Table S3) but
style length also contributed moderately on PC1 (loading = -0.33). The
second principal component (PC2) represented 25.05\% of the trait
variation and indicated a trade-off between low and high pollinator
dependence. We refer to this axis as the `pollinator dependence
trade-off'. The main driver of trait variation on PC2 was autonomous
selfing (loading = 0.85) but the other traits (except ovule number) also
made moderate contributions (loadings from 0.27 to 0.4; Supplementary
Table S3). We found that high pollinator dependence was associated with
larger and a higher number of flowers, greater plant height and longer
styles. In contrast, species with high levels of autonomous selfing
tended to have fewer and smaller flowers, had shorter styles and were
shorter in height. Further, PC3 explained a considerable amount of trait
variability (19.17\%) and the main contributors to this axis were style
length (loading = -0.66) and the degree of autonomous selfing (loading =
-0.51). The remaining traits, apart from ovule number, were moderately
correlated to changes on PC3 (loadings from -0.23 to -0.46;
Supplementary Table S3). Thus, because style length was correlated with
all traits on PC3 and was the main driver of trait variation, we refer
to this axis as the `style length trade-off'. Further, the pPCA with the
subset of species that had nectar and pollen quantity data showed that
nectar quantity (microlitres of nectar per flower) was positively
associated with flower size, style length and ovule number (PC1,
23.40\%); and pollen quantity (pollen grains per flower) was positively
correlated with flower number and plant height and negatively associated
with autonomous selfing (PC2, 21.67\%; Supplementary Fig. S6). This pPCA
explained similar variance with the first two principal components
(45.07\%) and similar associations of traits despite some variability in
the loadings (Supplementary Table S4).

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-1-1.pdf}
\caption{\label{fig:unnamed-chunk-1}\textbf{Fig. 1 \textbar{} Plant
life-history strategies.} Phylogenetically informed principal component
analysis (pPCA) of 1,236 plant species from 28 plant-pollinator networks
studies. The solid arrows indicate the direction of the different
quantitative traits (flower number, plant height, style length, flower
size, ovule number and level of autonomous selfing) across the two main
axes of trait variation. The length of the arrows indicate the weight of
the variables on each principal component and the labelled icons at
their end represent the extreme form of the trait continuum. The dashed
lines show the opposed direction of trait variation and the non-labelled
icons at their end illustrate the opposing extreme of the continuum.}
\end{figure}

We found that most categorical traits were statistically associated with
the first two axes of trait variation (Fig. 2 and Supplementary Table
S2). Flower symmetry, which was only associated with PC2 (Sum of squares
= 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar
provision, which was independent of PC1 and PC2 (PC1: Sum of squares =
0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83,
F-value = 1.43, \emph{P} = 0.23) showed lack of statistical association.
In addition, we found with Tukey test statistical differences between
the different levels of categorical traits in the trait space
(Supplementary Fig. S7). Regarding self compatibility, we found larger
differences on PC2 (i.e., species with unisexual flowers that were self
incompatibile were statistically differentiated from species with
partial or full self compatibility; Supplementary Fig. S7a and Fig.
S7b). Life forms differed statistically across both axes of trait
variation and followed a gradient of larger life forms (trees and
shrubs) with higher pollinator dependence to smaller ones (herbs) with
lower pollinator dependence (Supplementary Fig. S7c and Fig. S7d).
Consequently, lifespan also followed this gradient but perennial and
short lived species only differed statistically on PC2 (Supplementary
Fig. S7e and Fig. S7f). Species with unisexual flowers (monoecious and
dioecious) were clustered on both extremes of the first two principal
components and had the highest pollinator dependence and highest number
of flowers (Supplementary Fig. S7g and Fig. S7h). Moreover, we found
that the campanulate and capitulum flower shapes were differentiated
from tube, papilionaceous, open and brush shapes in the trait space. The
former morphologies had larger flowers and greater pollinator
dependence, while the latter had higher flower number and greater
autonomous selfing (Supplementary Fig. S7i and Fig. S7j). Regarding
flower symmetry, zygomorphic flowers were associated with lower levels
of pollinator dependence, whereas actinomorphic flowers had higher
levels of pollinator dependence (Supplementary Fig. S7k and Fig. S7l).

@@

\textbf{Phylogenetic signal of traits.} We found a strong phylogenetic
signal (\emph{P} \textless{} 0.01) in all quantitative traits
(Supplementary Table S5). The traits that showed the highest
phylogenetic signal were ovule number (\(\lambda = 1\)), pollen grains
per flower (\(\lambda = 1\)) and plant height (\(\lambda = 0.96\)),
followed by flower length (\(\lambda = 0.75\)), flower width
(\(\lambda = 0.73\)), number of flowers per plant (\(\lambda = 0.69\))
and nectar concentration (\(\lambda = 0.65\)). The traits that showed a
moderate phylogenetic signal were inflorescence width
(\(\lambda = 0.57\)), style length (\(\lambda = 0.49\)) and autonomous
selfing (\(\lambda = 0.34\)). Finally, microliters of nectar per flower
showed the lowest phylogenetic signal of all traits
(\(\lambda = 0.14\)).

\textbf{Visitation patterns.} The main axes of trait variation explained
little of the overall visitation rates (\(conditional R2 = 0.31\);
\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
interaction with the different floral visitors guilds (Fig. 3). All
floral visitors guilds visited plant species with higher pollinator
dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
3f). Furthermore, when running an additional model that separates the
most represented families of Anthophila-Hymenoptera (bees;
\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
family Apidae was the main driver of the observed patterns
(Supplementary Fig. S8).

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\textbf{Fig. 3 \textbar{} Visitation
rates across the three main axes of trait variation.} Fitted posterior
estimates of the number of visits made by the different floral visitors
guilds in relation to PC1, PC2 and PC3. Bees (a, b and c) and the rest
of guilds (d, e and f) were plotted separately for visualization
purposes. In addition, we trimmed the plotting area that was over the
95th percentile to improve visualisation. PC1 represents the flower
number - flower size trade-off, PC2 represents the pollinator dependence
trade-off and PC3, the style length trade-off.}
\end{figure}

@@

\textbf{Plant species functional roles.} The variance of the different
plant species level metrics was poorly explained by the three main axes
of trait variation (Supplementary Fig. S9; interaction frequency
\textasciitilde{} PCs, \(conditional R2 = 0.11\),
\(marginal R2 = 0.02\); normalized degree \textasciitilde{} PCs,
\(conditional R2 = 0.24\), \(marginal R2 = 0.02\); and, specialization
\textasciitilde{} PCs, \(conditional R2 = 0.37\),
\(marginal R2 = 0.03\)). Overall, the most notable trends were found on
PC1 and PC3 for interaction frequency and specialization. On the flower
number - flower size trade-off (PC1), interaction frequency was higher
for plant species with more flowers but was lower for plant species with
larger flowers. On PC1, specialization showed the opposite trend. On the
style length trade-off (PC3), interaction frequency was lower for plants
with shorter styles and lower autonomous selfing and higher for species
with longer styles and higher autonomous selfing. Again, specialization
showed the opposite trend to interaction frequency.

@@

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
\caption{\label{fig:unnamed-chunk-4}\textbf{Fig. 4 \textbar{} Trait
relevance on the plant species' functional roles.} Regression tree
analysis of interaction frequency (log-transformed), normalized degree
and specialization for the subset of species with quantitative data for
pollen and nectar traits. The superior value inside the node indicates
the mean value of the different species-level metric and the lower
value, the percentage of species that are considered in each node. Thus,
the top node has the mean value of the named trait for the 100\% of
species. Each node has a yes/no question and when the condition is
fulfilled, the branch turns to the `yes' direction and when not, to the
`no' direction. This rationale is followed in all the regression trees
as indicated in the first branch division of the topmost node of each
tree.}
\end{figure}

@@

Over 50\% of plant trait variation was captured by the flower number -
flower size and pollinator dependence trade-offs. Variation in these two
axes of trait variation appears to be associated with the commonly
described `fast-slow continuum' in
plant\textsuperscript{\protect\hyperlink{ref-salguero2016}{8}} and
animal\textsuperscript{\protect\hyperlink{ref-healy2019}{34}}
life-history strategies as indicated by the different floral and
reproductive traits associated with plant height, life form and
lifespan. The `slow' part of the continuum (i.e., tall trees and shrubs)
had plant species with many flowers, few ovules, higher pollinator
dependence, greater occurrence of self-incompatibility and more complex
breeding systems (e.g., monoecious and dioecious species). In contrast,
species that employed the `fast' strategy (i.e., short herbs), had fewer
flowers, more ovules, greater occurrence of self compatibility and lower
pollinator dependence. Further, on the first two axes of trait
variation, we found additional support for the previously described
positive association between outcrossing rate and floral
display\textsuperscript{\protect\hyperlink{ref-goodwillie2010}{24}}.
This trend was further confirmed when looking at the specific
correlation between floral display and autonomous selfing for our
dataset (see Supplementary Fig. S10).

Despite the low predictive power of the main axes of trait variation on
overall visitation patterns, we found commonalities among and within
floral visitors guilds across these axes that indicate the influence of
life-history strategies on floral visitation rate. For example, all
guilds showed an increasing trend of visitation on plant species with
higher pollinator dependence, which were also associated with larger
floral displays and greater pollen quantity (Fig. 1 and Supplementary
Fig. S6). This trend is consistent with previous plant-pollinator
studies that show higher visitation rates on species that make greater
reproductive
investment\textsuperscript{\protect\hyperlink{ref-hegland2005}{35}--\protect\hyperlink{ref-kaiser2014}{37}}.
In regard to the flower number - flower size and style length
trade-offs, different guilds showed contrasting visitation rates, which
could be associated with different pollination syndromes at a
macroecological scale. For instance, the guilds of bees and syrphids
were clearly associated with opposing life-strategies on PC1 and PC3
(Fig. 3) indicating a possible niche partitioning among these two
guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{38},\protect\hyperlink{ref-phillips2020}{39}}.
However, these plant-pollinator associations do not account for some of
the traits (i.e., pollen and nectar quantity) that had greater relevance
on the species network roles (Fig. 4) because of insufficient data
availability and lack of pollinator efficiency measurements for more
complete descriptions of the pollination
syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{13}}. In
any case, it is worth noting that this general pattern emerges in
field-measured plant-pollinator networks, where other local factors such
as species relative abundances, will surely explain part of the observed
variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{12},\protect\hyperlink{ref-vazquez2007}{40},\protect\hyperlink{ref-encinas2012}{41}}.
